\documentclass{letter}
\usepackage{hyperref}
\signature{Michael Georgariou III}
\address{8278 Station Village \\ Apt 2903 \\ San Diego, CA 92108}
\begin{document}

    \begin{letter}{Director \\ Doe \& Co \\ 35 Anthony Road
            \\ Newport \\ Ipswich IP3 5RT}
        \opening{To whom it may concern:}

        I am excited to submit my application for your [JOB TITLE] position. As 
        a software engineer with experience in both embedded systems and full-
        stack web development, I can be a valuable asset to the team.

        My time at Amazon has provided me the skills needed to be efficient and 
        productive as a software engineer. While there, I learned how to manage 
        time using Scrum. Being in both the team's on-call and Scrum master 
        rotations, I had an intimate knowledge of how a team should be run to 
        find success. I am proud to have made important contributions on my team 
        as well, such as writing feature design documents and owning multiple 
        critical product features. I'm sure all of the skills I've gained from 
        this will be helpful to [COMPANY NAME].
        
        In previous work at Aruba Networks, I had the unique opportunity of 
        working alongside many experienced engineers, working on projects under 
        their supervision and guidance. In school, I also focused on many 
        projects, including filesystem readers, weather stations, RISC-V based 
        microprocessors, and research.

        My past experience and projects have allowed me to apply the knowledge I
        have in the software engineering space. At my multiple positions as well 
        as throughout my education, I was able to demonstrate my ability to meet 
        deadlines, commit quality well-tested code, work with a team, and 
        communicate and document my work well. I'm confident these skills will 
        be put to good use at [COMPANY NAME].

        Thank you for your time and consideration. I look forward to your reply, 
        and talking with you further about the position.

        \closing{Yours truly,}

    \end{letter}
\end{document}
