%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemSingle}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}


% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://georgariou.com/}{\Large Michael Georgariou III}} 
    & Email : \href{mailto:3@georgariou.com}{3@georgariou.com}\\
  \href{https://georgariou.com/}{https://georgariou.com} 
    & Mobile : \href{tel:8313329962}{(831) 332-9962}\\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Amazon}{San Diego, CA}
      {Software Development Engineer II}{Jan. 2022 - Present}
      \resumeItemListStart
        \resumeItemSingle {
          Ran experiments to re-rank widgets across Amazon by weighing their
          return score, generating millions of daily impressions while
          decreasing total sales for highly-returned items and increasing
          total sales for other items
        }
        \resumeItemSingle {
          Implemented a new system which would display a "Frequently 
          Returned Item" badge on products in Amazon's catalog that met
          certain thresholds to qualify as a highly-returned item
        }
        \resumeItemSingle {
          Developed multiple web-apps from the ground up using the Spring Web 
          MVC framework and React.js, including full integration and unit
          testing, CI/CD pipelines, and alarms/ticketing for site failures
        }
        \resumeItemSingle {
          Owned and wrote several design documents for high-level and
          low-level technical implementations, which were implemented and 
          promoted to production by others following my designs
        }
        \resumeItemSingle {
          Led efforts to deprecate features, increasing team productivity and 
          decreasing operational burden, as well as supporting external teams'
          migrations away from the deprecated features
        }
        \resumeItemSingle {
          Mentored junior engineers and interns and helped them deliver 
          projects to production displayed on Amazon's site
        }
      \resumeItemListEnd
  
    \resumeSubheading
      {Hewlett-Packard Enterprise (Aruba Networks)}{Roseville, CA}
      {Systems/Software Engineer}{Jun. 2021 - Jan. 2022}
      \resumeItemListStart
        \resumeItemSingle {
          Led a newly-created Proto Support team to automate and simplify the
          engineering process when working with in-office hardware remotely,
          supporting around 100 engineers
        }
        \resumeItemSingle {
          Reworked the test framework led a code refactoring effort for a 
          new daemon being produced by my team
        }
      \resumeItemListEnd
      
    \resumeSubSubheading
      {Embedded Software Engineering Intern}{Jun. 2020 - Dec. 2020}
      \resumeItemListStart
        \resumeItemSingle {
          Assisted in creation of new switch mode that allowed for hub-like 
          functionality by disabling all switching and routing protocols,
          including writing feature tests and regression tests
        }
      \resumeItemListEnd
      
    \resumeSubSubheading
     {Software Engineering Intern}{Jun. 2019 - Aug. 2019}
     \resumeItemListStart
        \resumeItemSingle {
          Created an API for multiple daemons to access new column data 
          produced by a migration effort which determined whether or not
          a port has routing enabled, and refactored all existing code to
          use this API
        }
     \resumeItemListEnd
%-------------------------------------------
% I think it's finally time to retire the Sea Sweepers point on the resume :(
    % \resumeSubheading
    %   {Sea Sweepers Underwater Robotics}{Salinas, CA}
    %   {Lead Electrical and Software Engineer}{Jun. 2014 - Aug. 2017}
    %   \resumeItemListStart
    %     \resumeItemSingle {
    %       Implemented new systems for vehicle control and data transfer 
    %       through serial communication
    %     }
    %     \resumeItemSingle {
    %       Designed multiple PCBs to streamline the electrical design of the 
    %       vehicle
    %     }
    %     \resumeItemSingle {
    %       Engineered reliable communication protocol to ensure high speeds and 
    %       minimal loss of data using RS-232
    %     }
    %   \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

	\resumeSubheading
      {MPGameBoy}{}
      {Written in C, closed-source on GitHub, work in progress}{Oct. 2022 - Present}
      \resumeItemListStart
        \resumeItemSingle {
          Implemented the Nintendo GameBoy's architecture in portable C code
          to load and read ROMs for the console
        }
        \resumeItemSingle {
          Wrote CPU implementation, instruction handling, a debugger, and a
          tile-set viewer
        }
      \resumeItemListEnd

	\resumeSubheading
	  {Minls and Minget}{}
	  {Written in C}{Jun. 2021}
	  \resumeItemListStart
	    \resumeItemSingle {
        Created a filesystem reader for Minix, for use outside of the Minix 
        operating system, in portable C code
      }
	    \resumeItemSingle {
        Supported functions to list out the contents of a directory and print 
        the contents of a file
      }
	   \resumeItemListEnd
	  
	\resumeSubheading
	  {Portable Weather Station}{}
	  {Written in C for the MSP432}{May 2020}
      \resumeItemListStart
        \resumeItemSingle {
          Created libraries for four different weather sensors to easily
          interact with the MSP432 microprocessor
        }
        \resumeItemSingle {
          Implemented these libraries to display all the data on an LCD screen
        }
      \resumeItemListEnd
	  
	\resumeSubheading
      {The Otter XADC}{}
      {Written in C and SystemVerilog}{Mar. 2020}
      \resumeItemListStart
        \resumeItemSingle {
          Designed a microprocessor from scratch in SystemVerilog to run 
          assembly and C code on
        }
        \resumeItemSingle {
          Created a library to allow use of the given hardware’s XADC chip with 
          our microprocessor in C
        }
      \resumeItemListEnd
	  
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Polytechnic State University}{San Luis Obispo, CA}
      {Bachelor of Science in Computer Engineering;  GPA: 3.53}
      {Aug. 2017 -- Jun. 2021}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C/C++, Java, JavaScript, TypeScript, Python}
      \hfill
      \textbf{Technologies}{: Git, Unix, Vim, React.js, Spring}
    }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
